Verifying Demonstrations

### 2017-07-19 properties.tex
Adds short title for section auth, verif and priv
Works through privacy properties

\mode*
\section{Authenticity, verification and privacy}

@@

In voting, we have the following alternative requirements:
\begin{frame}
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\pause
\mode<presentation>{
  \begin{remark}
    P\ref{CoercionResistance} \(\implies\)
    P\ref{ReceiptFreeness} \(\implies\)
    P\ref{VotePrivacy}
  \end{remark}
}
\end{frame}
\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
\Cref{CoercionResistance} is probably not possible to achieve for protests:
e.g.\ Eve can simply physically bring Alice to a protest against her will.
This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

@@

A demonstration is very different from voting in one sense: Alice must be 
physically present and that very presence shows her support for the cause.
In voting, on the other hand, Alice has multiple options which are not revealed
by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof to the block chain, it must be unlinkable to 
Alice yet if Alice submits another proof, those two proofs must be linkable.

>>>>

\mode*
\section[Verification and privacy]{Authenticity, verification and privacy}

@@

In voting, we have the following requirements:
\begin{frame}
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\pause
\mode<presentation>{
  \begin{remark}
    P\ref{CoercionResistance} \(\implies\)
    P\ref{ReceiptFreeness} \(\implies\)
    P\ref{VotePrivacy}
  \end{remark}
}
\end{frame}
\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
\Cref{CoercionResistance} is probably not possible to achieve for protests:
e.g.\ Eve can simply physically bring Alice to a protest against her will.
This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

@@

A demonstration is very different from voting in one sense: Alice must be 
physically present and that very presence shows her support for the cause.
In voting, on the other hand, Alice has multiple options which are not revealed
by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof to the block chain, the proof must be 
unlinkable to Alice, yet, if Alice submits another proof, those two proofs must 
be linkable (due to eligibility verification, \cref{EligibilityVerif}).
E.g.\ Eve compromises Alice's device (and private keys).
Anyone can verify any proof.
With the inputs that Eve can extract from the published proof and the keys she 
can find on Alice's device, she should not be able to reproduce the same 
signatures on the proof.

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item Voting: different alternatives when participating.
      \item Protesting: participation implies the alternative.
    \end{itemize}
  \end{remark}

  \begin{idea}[P\ref{ReceiptFreeness} Receipt freeness]
    \begin{itemize}
      \item If Eve compromises Alice's device, she should not be able to use 
        it to verify that she participated.

      \item But Alice should not be able to participate twice.

      \item We need a signature scheme that cannot reproduce the same 
        signature when run on the same inputs.
    \end{itemize}
  \end{idea}
\end{frame}

\begin{frame}
  \begin{question}
    Will such a signature scheme solve both problems?
  \end{question}
  \begin{question}
    Is there such a signature scheme?
    Can we construct it?
  \end{question}
\end{frame}
